A Heuristic Approach towards Drawings of Graphs with High Crossing Resolution

### 2018-08-30 paper/paper.tex
minor change for consistency reasons.

In this section, we present drawings of the 5th and of the 9th graph given in the Graph Drawing contest 2017 that are produced by different variants of our algorithm and of the algorithms by Argyriou et al.~\cite{DBLP:journals/cj/ArgyriouBS13}, and by Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13}; see Figures~\ref{fig:graph5} and~\ref{fig:graph9}, respectively. Each variant was obtained by adjusting each of the aforementioned algorithms to optimize the crossing resolution, the angular resolution and the total resolution, respectively; the aesthetic criterion optimized by each variant is reported in the caption of its corresponding subfigure. As an initial drawing, we used for all algorithms the SmartOrganic layouts shown in Figure~\ref{fig:graph5And9-yfiles} computed with the yfiles library~\cite{DBLP:books/sp/04/WieseE004}.

\begin{figure}[htbp]
\centering
\subfloat[\label{fig:graph5-yfiles}{Graph 5}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-yfiles}
}
\hfil
\subfloat[\label{fig:graph9-yfiles}{Graph 9}]{
\centering
\includegraphics[width=0.3\textwidth]{graph9-yfiles}
}
\caption{SmartOrganic layouts by yFiles~\cite{DBLP:books/sp/04/WieseE004} of graphs 5 and 9 from last year's graph drawing contest.}
\label{fig:graph5And9-yfiles}
\end{figure}

\begin{figure}[htbp]
\centering
\subfloat[\label{fig:graph5-ourBest-cr}{Crossing Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourBest-crossing}
}
\hfill
\subfloat[\label{fig:graph5-ourBest-ar}{Angular Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourBest-angular}
}
\hfill
\subfloat[\label{fig:graph5-ourBest-tr}{Total Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourBest-total}
}
\hfill
\subfloat[\label{fig:graph5-ourRestricted-cr}{Crossing Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourRestricted-crossing}
}
\hfill
\subfloat[\label{fig:graph5-ourRestricted-ar}{Angular Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourRestricted-angular}
}
\hfill
\subfloat[\label{fig:graph5-ourRestricted-tr}{Total Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourRestricted-total}
}
\hfill
\subfloat[\label{fig:graph5-argyriou-cr}{Crossing Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-argyriou-crossing}
}
\hfill
\subfloat[\label{fig:graph5-argyriou-ar}{Angular Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-argyriou-angular}
}
\hfill
\subfloat[\label{fig:graph5-argyriou-tr}{Total Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-argyriou-total}
}
\hfill
\subfloat[\label{fig:graph5-huang-cr}{Crossing Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-huang-crossing}
}
\hfill
\subfloat[\label{fig:graph5-huang-ar}{Angular Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-huang-angular}
}
\hfill
\subfloat[\label{fig:graph5-huang-tr}{Total Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-huang-total}
}

>>>>

In this section, we present drawings of the 5th and of the 9th graph given in the Graph Drawing contest 2017 that are produced by different variants of our algorithm and of the algorithms by Argyriou et al.~\cite{DBLP:journals/cj/ArgyriouBS13}, and by Huang et al.~\cite{DBLP:journals/vlc/HuangEHL13}; see Figures~\ref{fig:graph5} and~\ref{fig:graph9}, respectively. Each variant was obtained by adjusting each of the aforementioned algorithms to optimize the crossing resolution, the angular resolution and the total resolution, respectively; the aesthetic criterion optimized by each variant is reported in the caption of its corresponding subfigure. As initial drawings for all algorithms, we used the layouts shown in Figure~\ref{fig:graph5And9-yfiles} that we computed with the SmartOrganic layouter of the yFiles library~\cite{DBLP:books/sp/04/WieseE004}.

\begin{figure}[htbp]
\centering
\subfloat[\label{fig:graph5-yfiles}{}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-yfiles}
}
\hfil
\subfloat[\label{fig:graph9-yfiles}{}]{
\centering
\includegraphics[width=0.3\textwidth]{graph9-yfiles}
}
\caption{Illustration of 
(a)~the 5th, and of
(b)~the 9th graph of the Graph Drawing contest 2017.}
\label{fig:graph5And9-yfiles}
\end{figure}

\begin{figure}[p]
\centering
\subfloat[\label{fig:graph5-ourBest-cr}{Crossing Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourBest-crossing}
}
\hfill
\subfloat[\label{fig:graph5-ourBest-ar}{Angular Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourBest-angular}
}
\hfill
\subfloat[\label{fig:graph5-ourBest-tr}{Total Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourBest-total}
}
\hfill
\subfloat[\label{fig:graph5-ourRestricted-cr}{Crossing Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourRestricted-crossing}
}
\hfill
\subfloat[\label{fig:graph5-ourRestricted-ar}{Angular Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourRestricted-angular}
}
\hfill
\subfloat[\label{fig:graph5-ourRestricted-tr}{Total Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-ourRestricted-total}
}
\hfill
\subfloat[\label{fig:graph5-argyriou-cr}{Crossing Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-argyriou-crossing}
}
\hfill
\subfloat[\label{fig:graph5-argyriou-ar}{Angular Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-argyriou-angular}
}
\hfill
\subfloat[\label{fig:graph5-argyriou-tr}{Total Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-argyriou-total}
}
\hfill
\subfloat[\label{fig:graph5-huang-cr}{Crossing Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-huang-crossing}
}
\hfill
\subfloat[\label{fig:graph5-huang-ar}{Angular Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-huang-angular}
}
\hfill
\subfloat[\label{fig:graph5-huang-tr}{Total Resolution}]{
\centering
\includegraphics[width=0.3\textwidth]{graph5-huang-total}
}
